Realization of a Decoherence-Free Subspace with Nitrogen-Vacancy Centers and $^{13}$C Nuclear Spins

### 2016-10-01 swap-nvst-paper/paper.tex
add derivation of nuclear positions from coherence data

%%% math, symbols, etc.
\usepackage{physics,braket,bm}
\renewcommand{\t}{\text} % text in math mode
\newcommand{\f}[2]{\dfrac{#1}{#2}} % shorthand for fractions
\newcommand{\p}[1]{\left(#1\right)} % square parenthesis
\renewcommand{\sp}[1]{\left[#1\right]} % square parenthesis
\renewcommand{\set}[1]{\left\{#1\right\}} % curly parenthesis
\renewcommand{\v}{\bm} % bold vectors
\newcommand{\uv}[1]{\hat{\v{#1}}} % unit vectors
\renewcommand{\c}{\cdot} % inner product
\newcommand{\bk}{\Braket} % shorthand for braket notation

@@

The AXY-$n$ sequence and the Hamiltonian in Eq. (\ref{eq:H_int})
allows for measurement of distinct frequencies $\omega_j$, hyperfine
couplings $A_j^\perp$, and ultimately the positions of $^{13}$C nuclei
via a coupling protocol ending in an NV coherence measurement,
outlined in \cite{wang2016positioning}. When on resonance with several
frequencies $\set{\omega_j}$ which the protocol cannot resolve, the NV
coherence after a time $t$ reads
\begin{align}
  \label{eq:L}
  L\p{t} = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t}.
\end{align}
After selecting an effective larmor frequency $\omega$ of interest via
the scanning protocol in \cite{wang2016positioning}, coherence
measurements as per Eq. (\ref{eq:L}) for different fourier components
$f_{k_{DD}}$ (or times $t$) are sufficient to determine the number of
nuclei with effective larmor frequency $\omega$. The protocol for
measuring $L$ can thus be used to identify a larmor pair.

After identifying a larmor pair, in order to locate the individual
nuclei in the pair we introduce an auxiliary magnetic decoupling field
$\tilde{\v B}_{\t{dec}}\p{t} = \v
B_{\t{dec}}\cos\p{\omega_{\t{dec}}t-\phi_{\t{dec}}}$. When
$\omega_{\t{dec}}$ is on resonance with the effective larmor frequency
$\omega$, the coherence in Eq. (\ref{eq:L}) is modified as
\begin{align}
  \label{eq:L_dec}
  \tilde L\p{t}
  = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t\cos\eta_j},
\end{align}
where the angle $\eta_j$ is determined by the directions
$\uv A_j^\perp$ and $\uv B_{\t{dec}}$, as well as the phases
$\phi_{DD}$ and $\phi_{\t{dec}}$ (see Supplementary Info
\ref{sec:addressing_pairs}). Measurements of the coherence $\tilde L$
as a function of fourier components $f_{k_{DD}}$ (or times $t$) and
phases $\phi_{DD}$ thus provides information about the directions
$\uv A_j^\perp$.

\fixme{How do we locate larmor pairs using Eq. (\ref{eq:L_dec})?}

@@

\pagebreak
\clearpage
\widetext \makeatletter
\begin{center}
  \large \bf Supplementary Information for ``\@title''
\end{center}
\setcounter{equation}{0} \setcounter{figure}{0} \setcounter{table}{0}
\setcounter{page}{1} \renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

@@

\section{Theory}

\subsection{Basic system model}

@@

\subsection{Dynamic decoupling and nuclear spin addressing}
\label{sec:dynamic_decoupling}

@@

When the harmonics of $F\p{t}$ are off resonance with all $\omega_j$
and $\omega_{DD}\gg A_j$ for all $j$, the secular approximation allows
one to neglect $\tilde H_{\t{int}}$ entirely. In this case, one can
apply an auxiliary magnetic field
$\tilde{\v B}_{\t{ctl}}\p{t}=\v
B_{\t{ctl}}\cos\p{\omega_{\t{ctl}}t-\phi_{\t{ctl}}}$ and shift into
the rotating frame of $H_{\t{nZ}}^{\t{eff}}$, much like the frame
shift between Eqs. (\ref{eq:S_H_sys_int_nZ}) and
(\ref{eq:S_H_int_no_DD}), to realize the Hamiltonian
\begin{align}
  \tilde H_{\t{sys}}^{\t{ctl}} =
  -\sum_j\gamma_j\v\B_{\t{ctl},j}\p{t}
  \cos\p{\omega_{\t{ctl}}t-\phi_{\t{ctl}}}\c\v I_j,
\end{align}
with $\v\B_{\t{ctl},j}\p{t}$ defined using $\v B_{\t{ctl}}$ and
$\v\omega_j$ the same way that $\v\A_j\p{t}$ was defined using
$\v A_j$ and $\v\omega_j$ in Eq. (\ref{eq:S_A_rot}), i.e. as
$\v B_{\t{ctl}}$ rotated about $\uv\omega_j$ by an angle $\omega_jt$:
\begin{align}
  \v\B_{\t{ctl},j}\p{t} = \v B_{\t{ctl},j}^\parallel
  + \v B_{\t{ctl},j}^\perp\cos\p{\omega_jt}
  + \v B_{\t{ctl},j}^{\perp\perp}\sin\p{\omega_jt},
\end{align}
where
\begin{align}
  \v B_{\t{ctl},j}^\parallel
  &\equiv \p{\v B_{\t{ctl}} \c\uv\omega_j}\uv\omega_j \\
  \v B_{\t{ctl},j}^\perp
  &\equiv \v B_{\t{ctl}} - \v B_{\t{ctl},j}^\parallel \\
  \v B_{\t{ctl},j}^{\perp\perp}
  &\equiv \uv\omega_j\times\v B_{\t{ctl}}^\perp.
\end{align}

@@

\subsection{Addressing larmor pairs}
\label{sec:addressing_pairs}

@@

In the frame of $H_{\t{nZ}}^{\t{eff}}=-\sum_j\v\omega_j\c\v I_j$, the
decoupling Hamiltonian becomes
\begin{align}
  \tilde H_{\t{dec}} = -\sum_j\gamma_j\v\B_{\t{dec},j}
  \c\v I_j \cos\p{\omega_rt-\phi_{\t{dec}}}
  \label{eq:S_H_dec_eff_full}
\end{align}
with
\begin{align}
  \v\B_{\t{dec},j} = \v B_{\t{dec},j}^\parallel
  + \v B_{\t{dec},j}^\perp\cos\p{\omega_j t}
  + \v B_{\t{dec},j}^{\perp\perp}\sin\p{\omega_j t}
\end{align}
and
\begin{align}
  \v B_{\t{dec},j}^\parallel
  &\equiv \p{\v B_{\t{dec}}\c\uv\omega_j}\uv\omega_j, \\
  \v B_{\t{dec},j}^\perp
  &\equiv \v B_{\t{dec}} - \v B_{\t{dec},j}^\parallel, \\
  \v B_{\t{dec},j}^{\perp\perp}
  &\equiv \uv\omega_j\times\v B_{\t{dec}}^\perp.
\end{align}
If $\omega_r,\omega_j\gg \gamma_jB_{\t{dec}}$, then we can neglect
$\v B_{\t{dec},j}^\parallel$ in Eq. (\ref{eq:S_H_dec_eff_full}) by the
secular approximation, and by the rotating approximation express
\begin{align}
  \tilde H_{\t{dec}} = -\sum_{j:\omega_j=\omega_r}
  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_{\t{dec}} +
  \v B_{\t{dec},j}^{\perp\perp}\sin\phi_{\t{dec}}}\c\v I_j.
\end{align}
Defining
\begin{align}
  \v\nu_j = \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_{\t{dec}}
  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_{\t{dec}}},
\end{align}
we can express
\begin{align}
  \tilde H_{\t{dec}} = -\sum_{j:\omega_j=\omega_r}\v\nu_j\c\v I_j.
\end{align}
The system Hamiltonian in the frame of $H_{\t{nZ}}^{\t{eff}}$ thus
takes the form
\begin{align}
  \tilde H_{\t{sys}}^{\t{dec}} = \tilde H_{\t{int}} + \tilde H_{\t{dec}}
  = \sum_{j:\omega_j=\omega_r}
  \p{h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
\end{align}

In the frame of $\tilde H_{\t{dec}}$, the entire system is governed by
the Hamiltonian
\begin{align}
  \tilde H_{\t{int}}^{\t{dec}} = \sum_{j:\omega_j=\omega_r}
  h_j^{\t{int}}\sigma_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
  \label{eq:S_H_int_dec_full}
\end{align}
where $\tilde{\v n}_j\p{t}$ is the unit vector $\uv n_j$ rotated about
$\uv\nu_j$ by $\nu_jt$, i.e.
\begin{align}
  \tilde{\v n}_j\p{t} = \v n_j^\parallel +
  \v n_j^\perp\cos\p{\nu_jt} + \v n_j^{\perp\perp}\sin\p{\nu_jt},
\end{align}
with
\begin{align}
  \v n_j^\parallel &\equiv \p{\uv n_j\c\uv\nu_j}\uv\nu_j, \\
  \v n_j^\perp &\equiv \uv n_j - \uv n_j^\parallel, \\
  \v n_j^{\perp\perp} &\equiv \uv\nu_j\times\uv n_j.
\end{align}
If $\omega_j\gg\nu_j\gg h_j^{\t{int}}$, the secular approximation
allows us to neglect $\v n_j^\perp$ and $\v n_j^{\perp\perp}$ in
Eq. (\ref{eq:S_H_int_dec_full}), leaving
\begin{align}
  \tilde H_{\t{int}}^{\t{dec}}
  = \sum_{j:\omega_j=\omega_r}
  \tilde h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv\nu_j,
  \label{eq:S_H_int_dec}
\end{align}
where
\begin{align}
  \tilde h_j^{\t{int}}
  = h_j^{\t{int}}\uv n_j\c\uv\nu_j.
\end{align}
Letting $\theta_j$ and $\theta_{\t{dec}}$ respectively be the angular
positions of $\uv A_j^\perp$ and $\uv B_{\t{dec}}^\perp$ in the plane
perpendicular to $\uv\omega_j$, we can say that
\begin{align}
  \tilde h_j^{\t{int}} = h_j^{\t{int}}\cos\eta_j,
\end{align}
where $\eta_j=\theta_j+\phi_{DD}-\p{\theta_{\t{dec}}+\phi_{\t{dec}}}$.

@@

\subsection{Coherent SWAP with a singlet-triplet qubit}

In the following section, we will consider an addressable larmor pair
with effective larmor frequencies $\omega$. We will use the basis
$\set{\ket\u\equiv\ket 0, \ket\d\equiv\ket{m_s}}$ for the spin states
of the NV electron, and the standard basis
$\set{\ket{\u\u}, \ket{\u\d}, \ket{\d\u}, \ket{\d\d}}$ for the spin
states of the nuclei. We will refer to the logical qubit consisting of
the basis states $\set{\ket{\u\d},\ket{\d\u}}$ as the anti-correlated
(AC) qubit, and the logical qubit consisting of the basis states
$\set{\ket\S,\ket\T}$ as the singlet-triplet (ST) qubit, where
\begin{align}
  \ket\S &\equiv \f1{\sqrt2}\p{\ket{\u\d}-\ket{\d\u}}, \\
  \ket\T &\equiv \f1{\sqrt2}\p{\ket{\u\d}+\ket{\d\u}}.
\end{align}

@@

\subsection{Robustness against noise}

@@

\section{Simulations and Results}

\subsection{Abundance of larmor pairs}

@@

\subsection{SWAP fidelities via AXY-$n$}

Discuss simulations and any relevant nuances therein. Present
histograms of $\SWAP^{\NV,\ST}$ fidelities and net operation times.

Note: the same simulations can also be used to generate similar
histograms (as well as other info) about other operations,
e.g. single-spin $\SWAP$ or $i\SWAP$ operations. Furthermore, the
simulations can, without any modification, reproduce results such as
Figure 2 in \cite{wang2016positioning} (``Positioning Nuclear Spins in
Interacting Clusters for Quantum Technologies and
Bio-imaging''). Minor additions to the codes might make them useful
for comparing the efficacy of different spin-addressing protocols. Is
there any interest in doing any of these things (for this paper or
elsewhere)?

@@

notes:

prove DFS

how to locate spins?
- identify larmor frequencies for C-13 nuclei
- identify a frequency with two spins
- locate two spins

perform elementary gate on one spin
implement PRX gates

>>>>

%%% math, symbols, etc.
\usepackage{physics,braket,bm,amssymb}
\renewcommand{\t}{\text} % text in math mode
\newcommand{\f}[2]{\dfrac{#1}{#2}} % shorthand for fractions
\newcommand{\p}[1]{\left(#1\right)} % square parenthesis
\renewcommand{\sp}[1]{\left[#1\right]} % square parenthesis
\renewcommand{\set}[1]{\left\{#1\right\}} % curly parenthesis
\renewcommand{\v}{\bm} % bold vectors
\newcommand{\uv}[1]{\hat{\v{#1}}} % unit vectors
\renewcommand{\c}{\cdot} % inner product
\newcommand{\bk}{\Braket} % shorthand for braket notation

@@

The AXY-$n$ sequence and the Hamiltonian in Eq. (\ref{eq:H_int})
allows for measurement of distinct frequencies $\omega_j$, hyperfine
couplings $A_j^\perp$, and ultimately the positions of $^{13}$C nuclei
via a coupling protocol ending in an NV coherence measurement,
outlined in \cite{wang2016positioning}. When on resonance with several
frequencies $\set{\omega_j}$ which the protocol cannot resolve, the NV
coherence after a time $t$ reads
\begin{align}
  \label{eq:L}
  L = \prod_j\cos\p{\f14 f_{k_{DD}}A_j^\perp t}.
\end{align}
After selecting an effective larmor frequency $\omega$ of interest via
the scanning protocol in \cite{wang2016positioning}, coherence
measurements as per Eq. (\ref{eq:L}) for different AXY-$n$ fourier
components $f_{k_{DD}}$ (or times $t$) are sufficient to determine the
number of nuclei with effective larmor frequency $\omega$. The
protocol for measuring NV coherence can thus be used to identify a
larmor pair.

After identifying a larmor pair, in order to locate the individual
nuclei in the pair we introduce an auxiliary magnetic decoupling field
$\tilde{\v B}_{\t{dec}}\p{t} = \v
B_{\t{dec}}\cos\p{\omega_{\t{dec}}t-\phi_{\t{dec}}}$. When
$\omega_{\t{dec}}$ is on resonance with the effective larmor frequency
$\omega$ of a larmor pair (and some simple conditions on
$\v B_{\t{dec}}$ are satisfied), the coherence in Eq. (\ref{eq:L}) can
be written as
\begin{align}
  \label{eq:L_dec}
  L = \f12\p{\cos\sp{2\xi\cos\alpha_+\cos\alpha_-}
  + \cos\sp{2\xi\sin\alpha_+\sin\alpha_-}}.
\end{align}
Here $\xi$ is a constant phase determined by $f_{k_{DD}}$, $A^\perp$,
and interaction time $t$; the angle $\alpha_-$ is determined by the
directions $\uv A_j^\perp$; and $\alpha_+$ is determined by the
directions $\uv A_j^\perp$ as well as $\phi_{DD}$, $\phi_{\t{dec}}$,
and $\uv B_{\t{dec}}$. Measurement of e.g.  $L\p{\xi,\phi_{DD}}$ thus
provides sufficient information to deduce the directions
$\uv A_j^\perp$, knowing which is necessary for individual nuclear
addressing protocols (see Supplementary Info section
\ref{sec:S_locating_pairs}).

@@

\pagebreak
\clearpage
\widetext \makeatletter
\begin{center}
  \large \bf Supplementary Information for ``\@title''
\end{center}
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\setcounter{section}{0}
\renewcommand{\thesection}{S.I. \Roman{section}}

@@

\section{Basic system model}

@@

\section{Dynamic decoupling and nuclear spin addressing}
\label{sec:S_dynamic_decoupling}

@@

When the harmonics of $F\p{t}$ are off resonance with all $\omega_j$
and $\omega_{DD}\gg A_j$ for all $j$, the secular approximation allows
one to neglect $\tilde H_{\t{int}}$ entirely. In this case, one can
apply an auxiliary magnetic field
$\tilde{\v B}_{\t{ctl}}\p{t}=\v
B_{\t{ctl}}\cos\p{\omega_{\t{ctl}}t-\phi_{\t{ctl}}}$ and shift into
the rotating frame of $H_{\t{nZ}}^{\t{eff}}$, much like the frame
shift between Eqs. (\ref{eq:S_H_sys_int_nZ}) and
(\ref{eq:S_H_int_no_DD}), to realize the Hamiltonian
\begin{align}
  \tilde H_{\t{sys}}^{\t{ctl}} =
  -\sum_j\gamma_j\v\B_{\t{ctl},j}\p{t}
  \cos\p{\omega_{\t{ctl}}t-\phi_{\t{ctl}}}\c\v I_j,
\end{align}
with $\v\B_{\t{ctl},j}\p{t}$ defined using $\v B_{\t{ctl}}$ and
$\v\omega_j$ the same way that $\v\A_j\p{t}$ was defined using
$\v A_j$ and $\v\omega_j$ in Eq. (\ref{eq:S_A_rot}), i.e. as
$\v B_{\t{ctl}}$ rotated about $\uv\omega_j$ by an angle $\omega_jt$:
\begin{align}
  \v\B_{\t{ctl},j}\p{t} = \v B_{\t{ctl},j}^\parallel
  + \v B_{\t{ctl},j}^\perp\cos\p{\omega_jt}
  + \v B_{\t{ctl},j}^{\perp\perp}\sin\p{\omega_jt},
\end{align}
where
\begin{align}
  \v B_{\t{ctl},j}^\parallel
  \equiv \p{\v B_{\t{ctl}} \c\uv\omega_j}\uv\omega_j,
  && \v B_{\t{ctl},j}^\perp
  \equiv \v B_{\t{ctl}} - \v B_{\t{ctl},j}^\parallel,
  && \v B_{\t{ctl},j}^{\perp\perp}
  \equiv \uv\omega_j\times\v B_{\t{ctl}}^\perp.
\end{align}

@@

\section{Addressing larmor pairs}
\label{sec:S_addressing_pairs}

@@

In the frame of $H_{\t{nZ}}^{\t{eff}}=-\sum_j\v\omega_j\c\v I_j$, the
decoupling Hamiltonian becomes
\begin{align}
  \tilde H_{\t{dec}} = -\sum_j\gamma_j\v\B_{\t{dec},j}
  \c\v I_j \cos\p{\omega_rt-\phi_{\t{dec}}}
  \label{eq:S_H_dec_eff_full}
\end{align}
with
\begin{align}
  \v\B_{\t{dec},j} = \v B_{\t{dec},j}^\parallel
  + \v B_{\t{dec},j}^\perp\cos\p{\omega_j t}
  + \v B_{\t{dec},j}^{\perp\perp}\sin\p{\omega_j t}
\end{align}
and
\begin{align}
  \v B_{\t{dec},j}^\parallel
  \equiv \p{\v B_{\t{dec}}\c\uv\omega_j}\uv\omega_j,
  && \v B_{\t{dec},j}^\perp
  \equiv \v B_{\t{dec}} - \v B_{\t{dec},j}^\parallel,
  && \v B_{\t{dec},j}^{\perp\perp}
  \equiv \uv\omega_j\times\v B_{\t{dec}}^\perp.
\end{align}
If $\omega_r,\omega_j\gg \gamma_jB_{\t{dec}}$, then we can neglect
$\v B_{\t{dec},j}^\parallel$ in Eq. (\ref{eq:S_H_dec_eff_full}) by the
secular approximation, and by the rotating approximation express
\begin{align}
  \tilde H_{\t{dec}} = -\sum_{j:\omega_j=\omega_r}
  \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_{\t{dec}} +
  \v B_{\t{dec},j}^{\perp\perp}\sin\phi_{\t{dec}}}\c\v I_j.
\end{align}
Defining
\begin{align}
  \v\nu_j = \f12\gamma_j\p{\v B_{\t{dec},j}^\perp\cos\phi_{\t{dec}}
  + \v B_{\t{dec},j}^{\perp\perp}\sin\phi_{\t{dec}}},
\end{align}
we can express
\begin{align}
  \tilde H_{\t{dec}} = -\sum_{j:\omega_j=\omega_r}\v\nu_j\c\v I_j.
\end{align}
The system Hamiltonian in the frame of $H_{\t{nZ}}^{\t{eff}}$ thus
takes the form
\begin{align}
  \tilde H_{\t{sys}}^{\t{dec}} = \tilde H_{\t{int}} + \tilde H_{\t{dec}}
  = \sum_{j:\omega_j=\omega_r}
  \p{h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv n_j - \v\nu_j\c\v I_j}.
\end{align}

In the frame of $\tilde H_{\t{dec}}$, the entire system is governed by
the Hamiltonian
\begin{align}
  \tilde H_{\t{int}}^{\t{dec}} = \sum_{j:\omega_j=\omega_r}
  h_j^{\t{int}}\sigma_\NV^z\v I_j\c\tilde{\v n}_j\p{t},
  \label{eq:S_H_int_dec_full}
\end{align}
where $\tilde{\v n}_j\p{t}$ is the unit vector $\uv n_j$ rotated about
$\uv\nu_j$ by $\nu_jt$, i.e.
\begin{align}
  \tilde{\v n}_j\p{t} = \v n_j^\parallel +
  \v n_j^\perp\cos\p{\nu_jt} + \v n_j^{\perp\perp}\sin\p{\nu_jt},
\end{align}
with
\begin{align}
  \v n_j^\parallel &\equiv \p{\uv n_j\c\uv\nu_j}\uv\nu_j, \\
  \v n_j^\perp &\equiv \uv n_j - \uv n_j^\parallel, \\
  \v n_j^{\perp\perp} &\equiv \uv\nu_j\times\uv n_j.
\end{align}
If $\omega_j\gg\nu_j\gg h_j^{\t{int}}$, the secular approximation
allows us to neglect $\v n_j^\perp$ and $\v n_j^{\perp\perp}$ in
Eq. (\ref{eq:S_H_int_dec_full}), leaving
\begin{align}
  \tilde H_{\t{int}}^{\t{dec}}
  = \sum_{j:\omega_j=\omega_r}
  \tilde h_j^{\t{int}}\sigma_\NV^z\v I_j\c\uv\nu_j,
  \label{eq:S_H_int_dec}
\end{align}
where
\begin{align}
  \tilde h_j^{\t{int}}
  = h_j^{\t{int}}\uv n_j\c\uv\nu_j.
\end{align}
Letting $\theta_j$ and $\theta_{\t{dec}}$ respectively be the angular
positions of $\uv A_j^\perp$ and $\uv B_{\t{dec}}^\perp$ in the plane
perpendicular to $\uv\omega_j$, we can say that
\begin{align}
  \tilde h_j^{\t{int}} = h_j^{\t{int}}\cos\p{\theta_j-\eta},
\end{align}
where $\eta=-\phi_{DD}+\theta_{\t{dec}}+\phi_{\t{dec}}$.

@@

\section{Identifying and locating larmor pairs}
\label{sec:S_locating_pairs}

Larmor pairs can be identified and located via NV coherence
measurements as in \cite{wang2016positioning}. When the AXY-$n$
sequence is on resonance with a larmor pair, the NV coherence reads
\begin{align}
  L = \cos^2\xi,
\end{align}
where the phase $\xi = h^{\t{int}}t = f_{k_{DD}}m_sA_j^\perp t/4$.
Applying a decoupling field as in section \ref{sec:S_addressing_pairs}
modifies $h_j^{\t{int}}\to h_j^{\t{int}}\cos\p{\theta_j-\eta}$, which
makes the NV coherence
($\eta=-\phi_{DD}+\theta_{\t{dec}}+\phi_{\t{dec}}$)
\begin{align}
  L
  = \cos\p{\xi\cos\sp{\theta_1-\eta}}\cos\p{\xi\cos\sp{\theta_2-\eta}}.
\end{align}
Defining
\begin{align}
  \alpha_- = \f12\p{\sp{\theta_1-\eta}-\sp{\theta_2-\eta}}
  = \f12\p{\theta_1-\theta_2},
  && \alpha_+ = \f12\p{\sp{\theta_1-\eta}+\sp{\theta_2-\eta}}
     = \f12\p{\theta_1+\theta_2} - \eta,
\end{align}
we can expand
\begin{align}
  L
  = \f12\p{\cos\sp{2\xi\cos\alpha_+\cos\alpha_-}
  + \cos\sp{2\xi\sin\alpha_+\sin\alpha_-}}.
\end{align}
When $\alpha_+$ is an integer multiple of $\pi/2$, this coherence
simplifies to ($n\in\mathbb Z$)
\begin{align}
  \label{eq:S_L_simplified}
  L\p{\alpha_+=n\pi} = \f12\p{1 + \cos\sp{2\xi\cos\alpha_-}},
  && L\p{\alpha_+=n\pi+\f\pi2}
     = \f12\p{1 + \cos\sp{2\xi\sin\alpha_-}}.
\end{align}
By collecting data on $L\p{\xi,\eta}$, one can identify fixed angles
$\bar\eta$ at which $L_{\bar\eta}\p\xi\equiv L\p{\xi,\bar\eta}$ takes
the form above. Knowing $L_{\bar\eta}\p\xi$ is then sufficient to
deduce the values of $\theta_1$ and $\theta_2$ up to a degeneracy
which does not affect nuclear spin addressing protocols. To find the
angles $\set{\theta_j}$ and understand this degeneracy, we first note
that changing these angles by $\pi$ as $\theta_j\to\theta_j+\pi$ does
not affect any protocols, so we can safely enforce all
$\theta_j\in\sp{0,\pi}$ and in turn $\alpha_\pm\in\sp{0,\pi}$. The
coherence $L\p{\xi,\eta}$ then takes the forms in
(\ref{eq:S_L_simplified}) when $\alpha_+\in\set{0,\pi/2}$, in which
case a fourier transform of $L_{\bar\eta}\p\xi$ can be used to
identify the coherence modes
\begin{align}
  \omega_L\p{\alpha_+=0}=2\xi\cos\alpha_-,
  && \omega_L\p{\alpha_+=\pi/2}=2\xi\sin\alpha_-,
\end{align}
and in turn the angles
\begin{align}
  \alpha_-\p{\alpha_+=0} = \acos\p{\f1{2\xi}\omega_L\p{\alpha_+=0}},
  && \alpha_-\p{\alpha_+=\f\pi2}
     = \asin\p{\f1{2\xi}\omega_L\p{\alpha_+=\f\pi2}}.
\end{align}
When $\alpha_+=0$, the angles $\theta_1$ and $\theta_2$ are then
\begin{align}
  \label{eq:S_nuclear_angles}
  \theta_1 = \bar\eta\p{\alpha_+=0} + \alpha_-\p{\alpha_+=0},
  && \theta_2 = \bar\eta\p{\alpha_+=0} - \alpha_-\p{\alpha_+=0},
\end{align}
The obvious problem with this recipe for $\set{\theta_j}$ is the fact
that measuring $L_{\bar\eta}\p\xi$ does not allow one to distinguish
the case of $\alpha_+=0$ from $\alpha_+=\pi/2$, as the form of
$L_{\bar\eta}\p\xi$ is identical in both cases. As it turns out, in
finding $\theta_1$ and $\theta_2$ via the prescription above, one is
free to simply assume without consequence that $\alpha_+=0$ whenever
the coherence $L_{\bar\eta}\p\xi$ takes the form in
(\ref{eq:S_L_simplified}). Incorrectly identifying the value of
$\alpha_+'=\pi/2-\alpha_+$ instead of $\alpha_+$ will result in the
deduction of $\alpha_-'=\pi/2-\alpha_-$ instead of $\alpha_-$. The
prescriptions in (\ref{eq:S_nuclear_angles}) then yield
\begin{align}
  \bar\eta\p{\alpha_+'=0} + \alpha_-'\p{\alpha_+'=0}
  = \sp{\bar\eta\p{\alpha_+=0} - \f\pi2}
  + \sp{\f\pi2 - \alpha_-\p{\alpha_+=0}}
  = \bar\eta\p{\alpha_+=0} - \alpha_-\p{\alpha_+=0} = \theta_2
\end{align}
and similarly
\begin{align}
  \bar\eta\p{\alpha_+'=0} - \alpha_-'\p{\alpha_+'=0} = \theta_1.
\end{align}
Using $\alpha_\pm'$ instead of $\alpha_\pm$ to find $\set{\theta_j}$
thus amounts to merely relabeling nuclei, which has no physical
consequence.

\section{Coherent SWAP with a singlet-triplet qubit}

In the following section, we will consider an addressable larmor pair
with effective larmor frequencies $\omega$. We will use the basis
$\set{\ket\u\equiv\ket 0, \ket\d\equiv\ket{m_s}}$ for the spin states
of the NV electron, and the standard basis
$\set{\ket{\u\u}, \ket{\u\d}, \ket{\d\u}, \ket{\d\d}}$ for the spin
states of the nuclei. We will refer to the logical qubit consisting of
the basis states $\set{\ket{\u\d},\ket{\d\u}}$ as the anti-correlated
(AC) qubit, and the logical qubit consisting of the basis states
$\set{\ket\S,\ket\T}$ as the singlet-triplet (ST) qubit, where
\begin{align}
  \ket\S \equiv \f1{\sqrt2}\p{\ket{\u\d}-\ket{\d\u}},
  &&  \ket\T \equiv \f1{\sqrt2}\p{\ket{\u\d}+\ket{\d\u}}.
\end{align}

@@

\section{Robustness against noise}

@@

\section{Abundance of larmor pairs}

@@

\section{SWAP fidelities via AXY-$n$}

\fixme{Discuss simulations and any relevant nuances therein. Present
  histograms of $\SWAP^{\NV,\ST}$ fidelities and net operation times.}

@@
